\documentclass[12pt]{amsart}

\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage[margin=1.1in, tmargin=1in, bmargin=1in]{geometry}

\pagestyle{myheadings}
%\markleft{Syllabus for Math 331, Spring 2020}
%\markright{Syllabus for Math 331, Spring 2020}

\newcommand{\spacer}{\vspace{.2cm}}
\newcommand{\svs}{\vspace{.1cm}}

\newcommand{\red}[1]{\textcolor{red}{#1}}
\definecolor{gold}{rgb}{0.80,0.68,0.00}\newcommand{\gold}[1]{\textcolor{gold}{#1}}

\begin{document}

\thispagestyle{empty}

\noindent\hrulefill
\begin{center}
\Large{\textsc{Math 331 Intro. to Real Analysis} }\quad \Large{\textsc{Fall 2021}} \\
\textsc{Study Guide}\\
\small{Created by Pierre-Olivier Paris{\'e}, Inspired by Malik Younsi's study guide}
\end{center}
\hrulefill \\

\section*{Before Each Class}
\textit{Lecture time is limited, so it must be used efficiently. Much of your learning must take place outside of the classroom. You are expected to be prepared as detailed below.}
	\begin{itemize}
	\item Review your notes from the class before, in order to make sure you understand the material that has already been covered.
	\item Read the appropriate section(s) of the textbook \textbf{before} the material is presented in class. This will greatly improve your understanding of the lectures.
	\end{itemize}
	
\section*{After Each Class}
\textit{For each hour in class, you should spend at least two or more hours studying outside the classroom.}
	\begin{itemize}
	\item Carefully reread your lecture notes. Review the examples that we did during the lecture to make sure you understand them.
	\item Attempt all of the homework problems and suggested problems.
	\item Try to not look at the solutions before attempting a problem!
	\item Don't hesitate to ask myself for help during my respective office hours. I will be happy to help you!
	\end{itemize}
	
\section*{Before an exam}
\textit{You won't have a lot of time to complete the problems on the exam (50min). Make sure to arrive prepared, so you don't unexpectedly loose time on a problem. Follow the tips below to prepare yourself.}
	\begin{itemize}
	\item Reread your lecture notes. Make sure you understand all the examples that we did during the lectures. You can try to redo the examples by yourself and compare your solutions to the one given in class. 
	\item Try to visualize the concepts by yourself. This will help you visualize the material that we covered.
	\item Summarize the material of each chapter in the lecture notes. In this way, you will have a great overview of all the material that was covered. You can use a mindmap to create your summary or just a short list.
	\item Retry the homeworks. The problems on the exam will find inspiration from the problems in the homework.
	\item Retry the suggested problems of each chapter. Make sure that you understand the problems that you got wrong. 
	\item Study with a friend or a group of friends; you can quiz each other on the material! This technic is really good to memorize the theorems and definitions.
	\end{itemize}

\end{document}